Title of the report

### 2011-12-06 doc/report/report.tex
documentation

\section{Related work}
>> Much more here, important!! comparisons.
Computational ling is active area for Swedish, there are many other Swedish parser,
but grammars?
Many of the parsers not ruled based, the most known one Malt\cite{malt} ... .
However has been two, about CLE\cite{cle} and what happened to it. Logic and translation
to Swedish, The spoken lang. translator\cite{cle2}. Wiren \cite{wiren}, cassSwe \cite{casswe}
Other Sw. parsers and grammars, evaluation of them? 
Other grammar frameworks.
% related and references work: CLE, Krasimirs book, CassSwe, GF book,SAG, gunlög,
% the multilingual treebank, Homse&Hinchcliff, Aarne i LILT

>>>>

\section{Related work}
>> Much more here, important!! comparisons.
Computational ling is active area for Swedish, there are many other Swedish parser,
but grammars?
Many of the parsers not ruled based, the most known one Malt\cite{malt} ... .
However has been two, about CLE\cite{cle} and what happened to it. Logic and translation
to Swedish, The spoken lang. translator\cite{cle2}. Wiren \cite{wiren}, cassSwe \cite{casswe}
Other Sw. parsers and grammars, evaluation of them? 
Other grammar frameworks.
HPSG\cite{hpsg} and lingo matrix\cite{lingomatrix}, English, Japanese, German, Greece, Spanish, Norweigan.
also Swedish: BiTSE\cite{stymne}, Stymne 2006, Swedish English translation, focusing on verb phrames, built on HPSG.
S\o rgaard and Haugereid, Scandinavian Grammar Matrix\cite{scandmatrix}
SweCore ??
Tag, Tree adjoining grammar, XTAG: English and Korean, Chinese? English: ongoing to get widecoverage grammar
under GPL. Translation to Korean.
% related and references work: CLE, Krasimirs book, CassSwe, GF book,SAG, gunlög,
% the multilingual treebank, Homse&Hinchcliff, Aarne i LILT
